\sysfull

### 2017-08-09 paper/systemdescription.tex

\sys is a new programming and execution model for intermittent computing on energy-harvesting devices. \sys addresses the challenges motivated in Section~\ref{sec:background} to make task-based intermittent programs {\em efficient}, {\em flexible}, and {\em programmable}. \sys accomplishes this goal with a constellation of a new programming model, compiler, and run time software system support, refer to Figure~\ref{fig:system_overview}.

@@

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Keyword & Description\\
		\hline\hline
		\texttt{task foo(){...}} & Task declaration\\
		\texttt{origin task foo(){...}} & Origin task declaration\\
		\texttt{next\_task()} & Transition to a new task\\
		\texttt{RP} & Read-protected variable\\
		\texttt{WP} & Write-protected variable\\
		\hline
	\end{tabular}
	\caption{Summary of \sys's programming model extensions}
	\label{tab:viper_syntax}
\end{table}

\noindent \textbf{\sys Memory Manager:} When the binary executes, \sys's runtime support affects its execution through {\em (virtualizing) memory manager} (described in Section~\ref{sec:memory_virtulaization}) and {\em (coalescing) task scheduler} (described in Section~\ref{sec:task_coalescing}). The \sys binary executes its tasks correctly, with consistent memory state, due to \sys's virtual memory mechanism. Relying on programmer or compiler annotation of accesses to memory locations that might be shared between tasks, \sys's memory virtualization {\em pages} these data to SRAM from FRAM as they are needed. Tasks operate, accessing SRAM only, demand-paging data to accommodate a SRAM smaller than FRAM\todo{Sentence unclear}{Brandon}. When a task completes, \sys commits modified, paged data back to its original FRAM location atomically ensuring subsequent tasks page in correct memory state.

>>>>

\sys is a new programming and execution model for intermittent computing on energy-harvesting devices. \sys addresses the challenges outlined in Section~\ref{sec:background} to make task-based intermittent programs {\em efficient}, {\em flexible}, and {\em programmable}. \sys accomplishes this goal with a constellation of a new programming model, compiler, and run time software system support, refer to Figure~\ref{fig:system_overview}.

@@

\begin{table}
	\centering
	\footnotesize
	\begin{tabular}{|c|c|}
		\hline
		Keyword & Description\\
		\hline\hline
		\texttt{task foo(){...}} & Task declaration\\
		\texttt{origin task foo(){...}} & Origin task declaration\\
		\texttt{next\_task()} & Transition to a new task\\
		\texttt{RP} & Read-protected variable\\
		\texttt{WP} & Write-protected variable\\
		\hline
	\end{tabular}
	\caption{Summary of \sys's programming model extensions.\todo{Revise this table (confusion with next\_task() function)}{Amjad/Przemek}}
	\label{tab:viper_syntax}
\end{table}

\noindent \textbf{\sys Memory Manager:} When the binary executes, \sys's runtime support affects its execution through a {\em (virtualizing) memory manager} (described in Section~\ref{sec:memory_virtulaization}) and a {\em (coalescing) task scheduler} (described in Section~\ref{sec:task_coalescing}). The \sys binary executes its tasks correctly, with consistent memory state, due to \sys's virtual memory mechanism. Relying on programmer or compiler annotation of accesses to memory locations that might be shared between tasks, \sys's memory virtualization {\em pages} these data to SRAM from FRAM as they are needed. Tasks operate, accessing SRAM only, demand-paging data to accommodate a SRAM smaller than FRAM\todo{Sentence unclear}{Brandon}. When a task completes, \sys commits modified, paged data back to its original FRAM location atomically ensuring subsequent tasks page in correct memory state.
